### 2019-05-13 README.Rmd
Added Travis logo to the README badge for Travis CI status

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Build Status](https://travis-ci.org/mcguinlu/robvis.svg?branch=master)](https://travis-ci.org/mcguinlu/robvis)

>>>>

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis)
